% xelatex
\documentclass{article}

\usepackage[utf8]{inputenc}
\usepackage{fontspec}
\setmainfont{Brill}

\usepackage{ot-tableau}
\usepackage[backend=biber, style=authoryear-icomp]{biblatex}
\usepackage{easylist}
\usepackage{hanging}
\usepackage{hyperref}
\usepackage{blindtext}
\usepackage{tipa}
\usepackage{cgloss4e}
\usepackage{gb4e}
\usepackage{qtree}
\usepackage{enumerate}
\usepackage{longtable}
\usepackage{textgreek}

\usepackage{enumitem}
\setlist[itemize]{itemsep=-5pt}

\title{i3 keybindings}
\author{}
\date{}

\begin{document}

\maketitle

\noindent
\texttt{Mod+F1} --- view this pdf. \\
\texttt{Mod+Shift+c} --- reload i3 config. \\
\texttt{Mod+Shift+r} --- restart i3.

\section*{window controls}

\vspace*{-.5\baselineskip}
\begin{itemize}
	\item \texttt{Mod+Shift+q} --- close focused window.
	\item \texttt{Mod+h} or \texttt{Mod+Left} --- focus left.
	\item \texttt{Mod+j} or \texttt{Mod+Down} --- focus down.
	\item \texttt{Mod+k} or \texttt{Mod+Up} --- focus up.
	\item \texttt{Mod+l} or \texttt{Mod+Right} --- focus right.
	\item \texttt{Mod+Shift+h} or \texttt{Mod+Shift+Left} --- move left.
	\item \texttt{Mod+Shift+j} or \texttt{Mod+Shift+Down} --- move down.
	\item \texttt{Mod+Shift+k} or \texttt{Mod+Shift+Up} --- move up.
	\item \texttt{Mod+Shift+l} or \texttt{Mod+Shift+Right} --- move right.
	\item \texttt{Mod+Shift+z} or \texttt{Mod+Control+Left} --- decrease window width.
	\item \texttt{Mod+Shift+u} or \texttt{Mod+Control+Down} --- decrease window height.
	\item \texttt{Mod+Shift+i} or \texttt{Mod+Control+Up} --- increase window height.
	\item \texttt{Mod+Shift+o} or \texttt{Mod+Control+Right} --- increase window width.
	\item \texttt{Mod+Shift{\small+}+} --- increase window gap size.
	\item \texttt{Mod+Shift{\small+}-} --- decrease window gap size.
	\item \texttt{Mod+Shift+BackSpace} --- reset window gap size.
	\item \texttt{Mod+f} --- toggle fullscreen mode for focused window.
	\item \texttt{Mod+Shift+Space} --- toggle floating mode for focused window.
	\item \texttt{Mod+Mouse} --- move or resize floating windows.
	\item \texttt{Mod+Space} --- move focused window to the center of the screen.
	\item \texttt{Mod+a} --- focus parent.
\end{itemize}

\section*{workspaces}

\vspace*{-.5\baselineskip}
\begin{itemize}
	\item \texttt{Mod+(Number)} --- go to the workspace with that number.
	\item \texttt{Mod+Shift+(Number)} --- move focused window to the workspace with that number.
\end{itemize}

\section*{screenshots}

\vspace*{-.5\baselineskip}
\begin{itemize}
	\item \texttt{Mod+Shift+s} --- take a screenshot using \texttt{flameshot}.
	\item \texttt{Print} --- takes a screenshot using \texttt{maim} and copies it to the clipboard.
	\item \texttt{Mod+Print} --- takes a screenshot of the active window using \texttt{maim} and copies it to the clipboard.
	\item \texttt{Shift+Print} --- takes a screenshot of the selected area using \texttt{maim} and copies it to the clipboard.
\end{itemize}

\section*{programs}

\vspace*{-.5\baselineskip}
\begin{itemize}
	\item \texttt{Mod+Return} --- spawn new terminal.
	\item \texttt{Mod+Shift+Return} --- spawn new terminal in floating mode.
	\item \texttt{Mod+Control+Return} --- spawn new terminal with the current directory as working directory.
	\item \texttt{Mod+e} --- nautilus.
	\item \texttt{Mod+Shift+e} --- ranger.
	\item \texttt{Mod+b} --- web browser (defaults to brave-browser).
	\item \texttt{Mod+Shift+b} --- web browser (incognito mode).
	\item \texttt{Mod+Control+b} --- qutebrowser.
	\item \texttt{Mod+s} --- spotify.

		\vspace*{-\baselineskip}
		\begin{itemize}
			\item \texttt{Mod{\small+}+} --- increase spotify volume.
			\item \texttt{Mod{\small+}-} --- decrease spotify volume.
		\end{itemize}\vspace*{-.5\baselineskip}
	\item \texttt{Mod+Control+s} --- shazam.
	\item \texttt{Mod+c} --- vscode.
	\item \texttt{Mod+t} --- teamspeak.
	\item \texttt{Mod+p} --- prismlauncher.
\end{itemize}

\section*{misc.}

\vspace*{-.5\baselineskip}
\begin{itemize}
	\item \texttt{Mod+w} --- show webcam in a floating window.
	\item \texttt{Mod+Shift+s} --- show the last notification in the dunst history.
	\item \texttt{Mod+Shift+p} --- toggle picom.
	\item \texttt{Mod+.} --- dmenu.
	\item \texttt{Mod+,} --- emoji picker.
	\item \texttt{Mod+Control+l} --- lock screen.
	\item \texttt{Mod+m} --- rotate through audio devices.
\end{itemize}

\end{document}
